%http://mohsaad.com/2018/09/10/Unsupervised-Depth/
\documentclass{article}
\usepackage[final]{nips_2017}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypograph
\title{Reproduction: Unsupervised Monocular Depth Estimation with Left-Right Consistency}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
	Andrija Djurisic\\
	Faculty of Mathematics, Belgrade\\
	\texttt{andrija.m.djurisic@gmail.com} \\
	%% examples of more authors
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \AND
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}

\begin{document}
	% \nipsfinalcopy is no longer used
	
	\maketitle
	
%	\begin{abstract}
%		The abstract paragraph should be indented \nicefrac{1}{2}~inch
%		(3~picas) on both the left- and right-hand margins. Use 10~point
%		type, with a vertical spacing (leading) of 11~points.  The word
%		\textbf{Abstract} must be centered, bold, and in point size 12. Two
%		line spaces precede the abstract. The abstract must be limited to
%		one paragraph.
%	\end{abstract}
	
\section{Introduction}
The most successful models that are solving depth estimation problem treat this task as supervised, meaning that large amount of data is required to successfully train the model. One such method is \textit{DispNet} [reference] which 
\section{Method}
\section{Experiments}


\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
	Remember that you can go over 8 pages as long as the subsequent ones contain
	\emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
	Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
	Exploring Realistic Neural Models with the GEneral NEural SImulation
	System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
	Neuroscience} {\bf 15}(7):5249-5262.

\end{document}